A Balanced Agent for Capture The Flag Pac-Man

### 2011-03-09 projectWriteup/paper.tex

\section{Inference}

\section{Particle Swarm Optimization}
\subsection{Algorithm}
\subsection{Theoretical Justification}
\subsection{Performance and Results}

>>>>

\section{Inference}
For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places more probability mass on positions that get them closer. Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever one moved before our agent who's analyzing his sensor readings). We're also very careful in our inference module about cases where we eat an opponent. When this happens, we update the probabilities to reflect that they're starting over at their initial position. And when an opponent is visible (i.e. in our line of sight), we update our probability mass to show that their position is exactly the one at which we see them. Once they're beyond our line of sight, we return to updating prior probabilities the same way we were before.
\section{Particle Swarm Optimization}
\subsection{Algorithm}
\subsection{Theoretical Justification}
\subsection{Performance and Results}
